---
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# quanteda.collocationsdev

[![CRAN Version](https://www.r-pkg.org/badges/version/quanteda)](https://CRAN.R-project.org/package=quanteda.collocationsdev)
[![Travis-CI Build Status](https://travis-ci.org/kbenoit/quanteda.collocationsdev.svg?branch=master)](https://travis-ci.org/kbenoit/quanteda.collocationsdev)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kbenoit/quanteda.collocationsdev?branch=master&svg=true)](https://ci.appveyor.com/project/kbenoit/quanteda.collocationsdev)
[![Coverage Status](https://img.shields.io/codecov/c/github/kbenoit/quanteda.collocationsdev/master.svg)](https://codecov.io/github/kbenoit/quanteda.collocationsdev?branch=master)

## About

An extension package with additional functionality for computing collocations statistics.  For developmental work.

## How to Install

```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("kbenoit/quanteda.collocationsdev") 
```

Because this compiles some C++ source code, you will need a compiler installed.
**If you are using a Windows platform**, this means you will need also to install
the [Rtools](https://CRAN.R-project.org/bin/windows/Rtools/) software available
from CRAN.  **If you are using macOS**, you will need to to install XCode,
available for free from the App Store, or if you prefer a lighter footprint set
of tools, [just the Xcode command line
tools](http://osxdaily.com/2014/02/12/install-command-line-tools-mac-os-x/ ),
using the command `xcode-select --install` from the Terminal.
    

## How to Use 

See `?collocationsdev`.
